Precise Weed and Maize classification through Convolutional Neuronal Networks

### 2017-07-06 PaperBCJ.tex
cambios_tabla

Samples were obtained from images captured in those maize fields , we considered to choose maize crops where we could visually discriminate the plants of the crop and the weed. Maize in stages V3-V7(3-7 leafs) \cite{Fassio} were used to take samples. To record the samples we centered the camera insuring that the capture shows all features of the maize plant, it was possible by monitoring the get of samples by an external display. An examples of the images captured are shown below. 
\\

@@

Inside of the shown parameters in the Table {table:1}, we considered the net who achieved the highest rate of accuracy and lowest rate of loss, clearly the cNET is the chosen due it shows a precission equal to human classification. The following picture shows the process of training of the cNET \\
Inside of the shown parameters in the Table \ref{table:2}, we considered the net who achieved the highest rate of accuracy and lowest rate of loss, clearly the cNET is the chosen due it shows a precission equal to human classification. The following picture shows the process of training of the cNET. \\

>>>>

Samples were obtained from images captured in those maize fields, we considered to choose maize crops where we could visually discriminate the plants of the crop and the weed. Maize in stages V3-V7(3-7 leafs) \cite{Fassio} were used to take samples. To record the samples we centered the camera insuring that the capture shows all features of the maize plant, it was possible by monitoring the get of samples by an external display. An examples of the images captured are shown below. 
\\

@@

Inside of the shown parameters in the Table {table:2}, we considered the net who achieved the highest rate of accuracy and lowest rate of loss, clearly the cNET is the chosen due it shows a precission equal to human classification. The following picture shows the process of training of the cNET \\
Inside of the shown parameters in the Table \ref{table:2}, we considered the net who achieved the highest rate of accuracy and lowest rate of loss, clearly the cNET is the chosen due it shows a precission equal to human classification. The following picture shows the process of training of the cNET. \\
